\section{Bibliografía}

\begin{itemize}

\item
(2015, 10). \textit{About - Leadership, Management Team, Global, History, Awards, Corporate Responsibility}. The Walt Disney Company. Obtenido 05, 2019, de \url{https://www.thewaltdisneycompany.com/about/#our-businesses}

\item
(2019, 03). \textit{2018-CSR-Report}. The Walt Disney Company. Obtenido 05, 2019, de \url{https://www.thewaltdisneycompany.com/wp-content/uploads/2019/03/2018-CSR-Report.pdf}

\item
\textit{Home - Disney Research. Disney Research}. Obtenido 05, 2019, de https://la.disneyresearch.com/

\item
\textit{Disney SCR}. Obtenido 05, 2019, de \url{https://twitter.com/DisneyCSR}

\item
(2018, 11). \textit{Q4 FY18 Earnings Report - q4-fy18-earnings}. The Walt Disney Company. Obtenido 05, 2019, de \url{https://www.thewaltdisneycompany.com/wp-content/uploads/2018/11/q4-fy18-earnings.pdf}

\item
S. (2013, 03). \textit{6 Crazy Niche Markets Discovered by Disney}. Parkeology Obtenido 05, 2019, de \url{http://www.parkeology.com/2013/03/7-crazy-niche-markets-disney-discovered.html}

\item
Ashraf, S. (2017, 09). \textit{Disney Park Secrets That Keep the Magic Alive (Gallery)}. The Daily Meal. Obtenido 05, 2019, de \url{https://www.thedailymeal.com/travel/disney-park-secrets-keep-magic-alive-gallery/slide-8}

\item
Bernardo, A. (2014, 04).\textit{ Innovación y animación: un repaso a la evolución de Disney}. La Unión. Obtenido 05, 2019, de \url{https://www.launion.com.mx/blogs/tecnologia/noticias/60282-innovacion-y-animacion-un-repaso-a-la-evolucion-de-disney.html}

\item
Brown, L.(2017, 12). \textit{Walt Disney Company SWOT Analysis \& Recommendations}. Paramore Institute. Obtenido 05, 2019, de \url{http://panmore.com/walt-disney-company-swot-analysis-recommendations}

\item
Elmansy, R. (2015, 06). \textit{Disney’s Creative Strategy: The Dreamer, The Realist and The Critic}. Designorate. Obtenido 05, 2019, de \url{https://www.designorate.com/disneys-creative-strategy/}

\item
Gartenberg, C. (2017, 12). \textit{Disney has acquired 21st Century Fox’s film and TV studios in a landmark deal}. The Verge. Obtenido 05, 2019, de \url{https://www.theverge.com/2017/12/14/16735502/disney-fox-deal-film-tv-studio-acquisition}

\item
Hirasuna, D. (2009, 08). \textit{Walt Disney’s Creative Organization Chart}. @Issue Journal of Business \& Design. Obtenido 05, 2019, de \url{https://atissuejournal.com/2009/08/07/walt-disney's-creative-organization-chart/}

\item
Jenkins, H. (2009, 12). \textit{The Revenge of the Origami Unicorn: Seven Principles of Transmedia Storytelling (Well, Two Actually. Five More on Friday)}. Confessions of an aca-fan. Obtenido 05, 2019, de \url{https://henryjenkins.org/blog/2009/12/the_revenge_of_the_origami_uni.html}

\item
Marr, B. (2017, 08). \textit{Disney Uses Big Data, IoT And Machine Learning To Boost Customer Experience}. Forbes. Obtenido 05, 2019, de \url{https://www.forbes.com/sites/bernardmarr/2017/08/24/disney-uses-big-data-iot-and-machine-learning-to-boost-customer-experience/}

\item
Pozzi, S. (2017, 02). \textit{Disney sale en auxilio de su parque temático en París}. El País. Obtenido 05, 2019, de \url{https://elpais.com/economia/2017/02/10/actualidad/1486738841_466812.html}

\item
Schlackman, S. (2014, 02). \textit{How Mickey Mouse Keeps Changing Copyright Law}. Artepreneur. Obtenido 05, 2019, de \url{https://alj.artrepreneur.com/mickey-mouse-keeps-changing-copyright-law/}

\item
Sturm, C. (2013, 10). \textit{7 innovaciones de Disney en sus 90 años de existencia}. FayerWayer. Obtenido 05, 2019, de \url{https://www.fayerwayer.com/2013/10/7-innovaciones-de-disney-en-sus-90-anos-de-existencia/}

\item
Williams, A. (2019, 03). \textit{Walt Disney Company’s Mission Statement \& Vision Statement (An Analysis)}. Paramore Institute. Obtenido 05, 2019, de \url{http://panmore.com/walt-disney-company-mission-statement-vision-statement-analysis}


\end{itemize}